\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

\author[1]{Guoying Deng}
\author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
\affil[1]{Sichuan University}
\affil[2]{University of Michigan, Ann Arbor}

@@

Our model is in line with the real world setting that the sellers are hard to know about which platform can bring how many buyers to the market but the buyers can search all the information available online to decide which house they can assess.

@@

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed which depends on the previous listing number and we can formulate it as a AR(1) model specified by:

\begin{equation}
  \kappa_{i, t} = \rho_{i} \kappa_{i-1, t} + \epsilon_{i, t}, \label{eq:ar1}
\end{equation}

where $\rho_i$ is the parameter and $\varepsilon_{i, t} \sim \mathcal{N}(0, \sigma_{i, t}^2)$. We can assume that the price of the house is determined by the hedonic pricing model, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.

The number of two types of brokerages are characterized by $B_{1, i}$ and $B_{2, i}$, respectively. The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{1, t}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{1, t}^2} > 0$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.

>>>>

\author[1]{Guoying Deng}
\author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
\affil[1]{School of Economics, Sichuan University, China}
\affil[2]{Department of Economics, University of Michigan, United States}

@@

Our model is in line with the real world setting that the sellers are hard to predict which platform can bring how many buyers to their house but the buyers can search all the information available online to decide which house they are interersted in.

@@

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed. Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market. We can denote the number of two types of brokerages by $B_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{B_{i, i}}{B_{i, 1} + B_{i, 2}}$.

We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.

The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{j}^2} > 0$ where $j \in \{1, 2\}$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.

We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
